\documentclass[oneside]{memoir}

\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}

\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhf[FC]{\thepage of \pageref{LastPage}}

\usepackage{fontspec}
\setmainfont{Gentium Book Basic}

\usepackage{hyperref}
\newdimen\longline
\longline=\textwidth\advance\longline-4cm

\def\LayoutTextField#1#2{#2} % override default in hyperref

\def\lbl#1{\hbox to 4cm{#1\dotfill\strut}}%
\def\labelline#1#2{\lbl{#1}\vbox{\hbox{\TextField[name=#1,width=#2,bordercolor=]{\null}}\kern2pt\hrule}}

\def\q#1{\hbox to \hsize{\labelline{#1}{\longline}}\vskip1.4ex}

\begin{document}
\section*{\Huge Advance Directive}\label{advance-directive}

\subsection{1. Durable power of attorney for health care}\label{durable-power-of-attorney-for-health-care}

\subsubsection{Creation of durable power of attorney for health care}\label{creation-of-durable-power-of-attorney-for-health-care}

I intend to create a power of attorney (Health Care Agent) by appointing the person or persons designated herein to make health care decisions for me to th extent that I could make such decisions for myself if I was capable of doing so, as recognized by Washington law. This power of attorney shall become effective when I become disabled and I cannot make health care decisions for myself as determined by my attending physician or designee, such as if I am unconscious, or if I am otherwise temporarily or permanently incapable of making health care decisions. The Health Care Agent's power shall cease if and when I regain my capacity to make health care decisions.

\subsubsection{Designation of Health Care Agent and alternate agents}\label{designation-of-health-care-agent-and-alternate-agents}

If my attending physician or his or her designee determines that I am not capable of giving informed consent to health care, I, \emph{Madison Scott-Clary}, designate and appoint:

\begin{quote}
    James Daniel Clary\\
    6811 Commercial Ave.\\
    Everett, WA 98203\\
    720-280-9766\\
    JDClary101@gmail.com
\end{quote}

\noindent as my attorney-in-fact (Health Care Agent) by granting him the Durable Power of Attorney for Health Care recognized in Washington law and authorize him to consult with my physicians about the possibility of my regaining the capacity to make treatment decisions and to accept, plan, stop, and refuse treatment on my behalf with the treating physicians and health personnel.

\vspace{1ex}

\noindent In the event that \emph{James Daniel Clary} is unable or unwilling to serve, I grant these powers to:

\begin{quote}
    Russel Reed\\
    641 Turnbuckle Dr \#1709\\
    Redwood City, CA 94063\\
    501-680-1371\\
    forneuslex@gmail.com
\end{quote}

\noindent In the event that both \emph{James Daniel Clary} and \emph{Russel Reed} are unable or unwilling to serve, I grant these powers to:

\begin{quote}
    Donna Karr\\
    303-551-1308\\
    donna.karr@gmail.com
\end{quote}

\subsubsection{General statement of authority granted}\label{general-statement-of-authority-granted}

My Health Care Agent is specifically authorized go give informed consent for health care treatment when I am not capable of doing so. This includes but is not limited to consent to initiate, continue, discontinue, or forgo medical care and treatment including artificially supplied nutrition and hydration, following and interpreting my instructions for the provision, withholding, or withdrawing of life-sustaining treatment , which are contained in any Health Care Directive or other form of ``living will'' I may have executed or elsewhere, and to receive and consent to the release of medical information. When the Health Care Agent does not have any stated desires or instructions for me to follow, they shall act in my best interest in making health care decisions.

\newpage

\noindent The above authorization to make health care decisions does not include the following absent a court order:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Therapy or other procedure given for the purpose of inducing convulsion;
\item
  Surgery solely for the purpose of psychosurgery;
\item
  Commitment to or placement in a treatment facility for the mentally ill, except pursuant to Chapter 71.05 RCW;
\item
  Sterilization.
\end{enumerate}

I hereby revoke any prior grants of durable power of attorney for health care.

\subsubsection{Special provisions}\label{special-provisions}

\emph{None}

\subsubsection{Signatures}\label{signatures}

Dated this \emph{ninth} day of \emph{April, 2018}.

\vspace{1ex}

\noindent Grantor: \emph{Madison Scott-Clary}

\begin{Form}
    \q{Grantor's signature}
\end{Form}

\emph{Note:} Washington state requires this directive to be notarized \emph{or} witnessed by two different witnesses.

\begin{quote}
    \textbf{I certify that I know or have satisfactory evidence that the GRANTOR, \emph{Madison Scott-Clary} signed this instrument and acknowledged it to be her free and voluntary act for the uses and purposes mentioned in the instrument.}
\end{quote}

\begin{Form}
    \q{Witness 1}
    \q{Witness 2}
\end{Form}

\emph{Witness requirements:} The witnesses to this document must be competent and must \emph{not} be:

\begin{itemize}
\tightlist
\item
  Home care providers for the individual completing this document;
\item
  Care providers at an adult family home or long-term care facility if you live there; or
\item
  Related to you or the designated Health Care Agent by blood, marriage, or state registered domestic partnership.
\end{itemize}

\newpage

\subsection{2. Health Care Directive}\label{health-care-directive}

Directive made this \emph{ninth} day of \emph{April, 2018}.

\vspace{1ex}

\noindent I, \emph{Madison Scott-Clary}, being of sound mind, willfully and voluntarily make known my desire that my dying shall not be artificially prolonged under the circumstances set forth below and do hereby declare that:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  If at any time I should have an incurable and irreversible condition certified to be a terminal condition by my attending physician, and where the application of life-sustaining treatment would serve only to artificially prolong the process of my dying, I direct that such treatment be withheld or withdrawn, and that I be permitted to die naturally. I understand that ``terminal condition'' means an incurable and irreversible condition caused by injury, disease, or illness that would, within reasonable medical judgment, cause death within a reasonable period of time in accordance with accepted medical standards.
\item
  If I should be in an irreversible coma or persistent vegetative state, or other permanent unconscious condition as certified by two physicians, and from which those physicians believe that I have no reasonable probability of recover, I direct that life-sustaining treatment be withheld or withdrawn.
\item
  If I am diagnosed to be in a terminal or permanent unconscious condition, I want artificially administered nutrition and hydration to be withdrawn or withheld the same as other forms of life-sustaining treatment. I understand artificially administered nutrition and hydration is a form of life-sustaining treatment in certain circumstances. I request all health care providers who care for me to honor this directive.
\item
  In the absence of my ability to give directions regarding the use of such life-sustaining procedures, it is my intention that this directive shall be honored by my family, physicians, and other health care providers as the final expression of my fundamental right to refuse medical or surgical treatment, and also honored by an person appointed to make these decisions for me, whether by durable power of attorney or otherwise. I accept the consequences of such refusal.
\item
  I understand the full import of this directive and I am emotionally and mentally competent to make this directive. I also understand that I may amend or revoke this directive at any time.
\item
  I make the following additional directions regarding my care: \emph{None}.
\end{enumerate}

\begin{Form}
    \q{Signed}
\end{Form}

\begin{quote}
    \textbf{The declarer has been personally known to me and I believe her to be of sound mind. In addition, I am not the attending physician, an employee of the attending physician or health care facility in which the declarer is a patient, or any person who has a claim against any portion of the estate of the declarer upon the declarer's decease at the time of the execution of the directive.}
\end{quote}

\begin{Form}
    \q{Witness 1}
    \q{Witness 2}
\end{Form}

\end{document}
