\documentclass[oneside]{memoir}

\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}

\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhf[FCE,FCO]{\thepage of \pageref{LastPage}}

\usepackage{fontspec}
\setmainfont{Gentium Book Basic}

\usepackage{hyperref}
\newdimen\longline
\longline=\textwidth\advance\longline-4cm

\def\LayoutTextField#1#2{#2} % override default in hyperref

\def\lbl#1{\hbox to 4cm{#1\dotfill\strut}}%
\def\labelline#1#2{\lbl{#1}\vbox{\hbox{\TextField[name=#1,width=#2]{\null}}\kern2pt\hrule}}

\def\q#1{\hbox to \hsize{\labelline{#1}{\longline}}\vskip1.4ex}
\begin{document}

\section*{Last Will and Testament of Madison Jesse Scott-Clary}\label{last-will-and-testament-of-madison-jesse-scott-clary}

I, Madison Jesse Scott-Clary, being of sound mind, do hereby make, publish, and declare this to be my last will and testament, hereby revoking all wills and codicils by me heretofore made.

\subsection*{Article 1: Representatives and Named Beneficiaries}\label{article-1-representatives-and-named-beneficiaries}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  James Clary shall be my personal representative in the execution of my estate.
\item
  The named beneficiares are as follows:

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    ``The Polycule'', in this document, refers to:

    \begin{itemize}
    \tightlist
    \item
      James Clary --- Husband --- Everett, WA
    \item
      Russel Reed --- Partner --- Redwood City, CA
    \item
      Conor McKeown --- Partner --- Leicester, Leicestershire, UK
    \end{itemize}
  \item
    Parents:

    \begin{itemize}
    \tightlist
    \item
      Donna Karr --- Mother --- Tulchas, NM
    \item
      Ronald Scott --- Father --- Lakewood, CO
    \end{itemize}
  \end{enumerate}
\item
  The Polycule shall have the right to appoint a literary executor as a representative with the understanding that they will abide by my intellectual property wishes set forth in Article 4.
\end{enumerate}

\subsection*{Article 2: Responsibilities and Obligations}\label{article-2-responsibilities-and-obligations}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Dogs:} James Clary shall assume full responsibility for our dogs. Should he be unable or unwilling to claim such, responsibility will fall to Donna Karr.
\end{enumerate}

\subsection*{Article 3: Assets}\label{article-3-assets}

\subsubsection*{Section 1: Property}\label{section-1-property}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  All property held jointly through Joint Tenancy or Tenants in Common with James Clary shall revert solely to him. This should be:

  \begin{itemize}
  \tightlist
  \item
    6216 Becker Ln., Loveland, CO 80538
  \item
    615 Andrea St., Fort Collins, CO 80524
  \item
    Hyundai Ioniq (car)
  \end{itemize}
\end{enumerate}

\subsubsection*{Section 2. Physical Assets}\label{section-2.-physical-assets}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Beneficiaries and friends at the discretion of The Polycule may keep \emph{no more than three items each} as mementos under the following terms:

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    This does not include laptops (see \emph{article 3, section 3} below).
  \item
    Items may be grouped sensibly (e.g: a camera body and its lenses in a camera bag).
  \item
    All three items must be able to be carried at once.
  \item
    Yes, James, this means you too. You have two estates already in the house.
  \end{enumerate}
\item
  \emph{All} remaining physical assets are to be sold, donated, or disposed of responsibly.

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    All funds from sold assets are to be treated as liquid assets under \emph{article 3, section 6}.
  \item
    Beneficiaries may not receive any remaining assets through sale, donation, or disposal. Please, James, get rid of my stuff for real.
  \end{enumerate}
\item
  To the following, above and beyond the ``three each'' clause:

  \begin{itemize}
  \tightlist
  \item
    To The Polycule: you have your proxy foxes and cats. You may have your proxy selves with my blessing.
  \item
    To James Clary (Everett, WA): you may have my collar. It was always yours.
  \item
    To Russel Reed (Redwood City, CA): all my music on physical media. All CDs, vinyl, and the one cassette tape I own, plus any sheet music you may want. You became the musical connection in my life.
  \item
    To Conor McKeown (Leics, UK): every single corgi-themed thing I owned. You're my number one best corgi, after all.
  \item
    To Justin Coffman (Charlotte, NC (I think)): my leash, which you bore so well.
  \item
    To Cullen Mahaney (Charlotte, NC (I think)): my copy of the comic \emph{Pies}, in which nothing is said.
  \item
    To Jamie Culpon (San Jose, CA): my hard-bound, gold-trimmed copy of \emph{Dune}, in the hopes that it keeps giving you strange and wonderful thoughts about the bene geserit.
  \item
    To Paul Rapoport (Chicago, IL): my copy of \emph{S}. Perhaps the story will be even more complete if you have two of them.
  \item
    To Kevin Frane (San Jose, CA): my two pieces of brush calligraphy wall art. One is a blessing for your home, and the other a poem.
  \item
    To Alex Osaki (Berlin, Germany): my BitBucket account, which hosts raw dumps of all Furry Survey data, for you to do with what you please, and my everlasting gratitude for your trust.
  \item
    To members of The Blazewing Eyrie and Transliminal Beta (Seattle, WA): my wand, knife, and Fellowship materials, to deconsecrate and destroy, bury, or keep. In payment for this and the joy you brought me, you're also welcome to my stock of Christmas Mead.
  \end{itemize}
\end{enumerate}

\subsubsection*{Section 3: Digital Assets}\label{section-3-digital-assets}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Digital assets are to be transferred off of my laptops and phones onto an external drive, and each laptop is to be wiped and donated or sold. I lived and worked on the damn things, get rid of them now that I'm gone.
\item
  The Polycule can decide what to keep and not from those external copies.
\end{enumerate}

\subsubsection*{Section 4: Online Presence}\label{section-4-online-presence}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  No posts, messages, or content are to be made on my behalf.
\item
  Many online services have rules and regulations surrounding death of an account holder. These are to be honored above my wishes.
\item
  Dropbox will delete an account after 90 days of inactivity. This is to be allowed with the following exceptions (note that per the transfer in \emph{article 3, section 3}, this will happen anyway):

  \begin{itemize}
  \tightlist
  \item
    The \texttt{commissions} folder in there contains art; feel free to snag that.
  \item
    The \texttt{Thurston} folder contains documents that Thurston Howl Publications may need. Send this folder to them the address in the notification document specified in \emph{article 6, section 1}.
  \item
    The \texttt{HYBRID} folder contains all documents pertaining to the operation of Hybrid Ink, LLC minus the source for Hybrid Ink projects such as \texttt{hybrid.ink} and \texttt{pubtracker}, and is to be managed per \emph{article 3, section 7}.
  \end{itemize}
\item
  Twitter account to be left as a memorial and warning to others against spending too much time online shitposting.
\item
  Mastodon account to be left as is.
\item
  Telegram account self-destructs after six months.
\item
  Slack does not have a death policy, but do try to get in touch with the admins of the two Slacks I'm on (Chipotle on the Writers' Guild slack, and Rattz or zander on the postfurry slack) and let them know to deactivate my account.
\end{enumerate}

\subsubsection*{Section 5: Hosted Assets}\label{section-5-hosted-assets}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Assets hosted on GitHub will remain there indefinitely as a matter of course.
\item
  There are two servers hosted by Linode. The \texttt{work} server may be terminated. \texttt{alopex} is to be left running for at least one year, as it hosts publicly available content such as \texttt{polycul.es}, \texttt{refs.express}, etc.
\item
  Dreamhost hosts DNS for all domains, as well as some sites such as {[}adjective{]}{[}species{]}, and will thus need to be kept paid for at least one year.
\item
  Domains are owned through NameCheap and are to be kept registered for at least one year.
\end{enumerate}

\subsubsection*{Section 6: Liquid Assets}\label{section-6-liquid-assets}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Upon execution of this will and the closing of the estate, all remaining liquid assets are to be either:

  \begin{itemize}
  \tightlist
  \item
    held in the trust of a foundation aiming to help with medical gender transition (hormones, therapy, surgery, etc). \emph{Or}
  \item
    donated to individuals through the crowdfunding sites YouCaring.com and GoFundMe.com requesting financial help for medical gender transition (hormones, therapy, surgery, etc).
  \end{itemize}
\end{enumerate}

\subsubsection*{Section 7: Hybrid Ink Assets}\label{section-7-hybrid-ink-assets}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  I have sole ownership of Hybrid Ink, LLC.
\item
  All authors with accepted projects must be notified of my death with a link to a publicly available obituary or news article.
\item
  There are two options:

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    All active contracts may be terminated by means of a signed termination agreement between my estate and the other party and the business to be shuttered. In this instance:

    \begin{itemize}
    \tightlist
    \item
      all products must be unlisted from the Gumroad, Amazon, and any other stores;
    \item
      any royalty payments must be made for up to one year; \emph{and}
    \item
      contracts and termination agreements kept for at least five years.
    \end{itemize}
  \item
    Ownership of the business is to be transferred wholesale to another party through sale, gift, or inheritance. In this instance:

    \begin{itemize}
    \tightlist
    \item
      contracts are to remain in force for their duration with unaltered terms attested to by a signed agreement with the new owner and the other party, with the option for the other party to terminate their agreement; \emph{and}
    \item
      all profits from such a sale are to be donated or held in accordance with \emph{article 3, section 6}.
    \end{itemize}
  \end{enumerate}
\end{enumerate}

\subsection*{Article 4: Intellectual Property}\label{article-4-intellectual-property}

\subsubsection*{Section 1: General Licensing}\label{section-1-general-licensing}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  All intellectual property should be licensed under a \href{https://creativecommons.org/licenses/by-sa/4.0/}{Creative Commons Attribution-ShareAlike 4.0 International license} or, in the case of software source code, an \href{https://opensource.org/licenses/MIT}{MIT License}.
\item
  These licenses shall not replace or infringe upon existing licenses held by other parties.
\end{enumerate}

\subsubsection*{Section 2: Publishing of Works}\label{section-2-publishing-of-works}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Works may be published and sold in such a way that does not infringe upon the license in \emph{article 4, section 1}.
\item
  The royalties from any such publications are to be donated or held in accordance with \emph{article 3, section 6}.
\end{enumerate}

\subsubsection*{Section 3: Existing Publications:}\label{section-3-existing-publications}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Royalties due from existing publications are to be donated or held in accordance with \emph{article 3, section 6}.
\end{enumerate}

\subsubsection*{Section 4: Editorial Work}\label{section-4-editorial-work}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Editorial projects such as but not limited to {[}adjective{]}{[}species{]} and Post-Self are to remain as is, with the option of a new editor stepping up.
\item
  In the case of a new editor, the licensing structure is to remain the same:

  \begin{enumerate}
  \def\labelenumii{\arabic{enumii}.}
  \tightlist
  \item
    All previous publications will retain their existing licenses.
  \item
    All new publications will use the license of the site.
  \item
    The license of the site will use or remain \href{https://creativecommons.org/licenses/by-sa/4.0/}{Creative Commons Attribution-ShareAlike 4.0 International license}
  \end{enumerate}
\end{enumerate}

\subsection*{Article 5: Remains}\label{article-5-remains}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  I am an organ donor. Any and all possible organs may be donated.
\item
  An autopsy may be performed.
\item
  After any and all such donations and/or autopsies have been made, my remains are to be cremated.
\item
  What is to be done with my ashes is up to The Polycule and my parents.
\item
  No physical monument of any type is to be erected or placed using my estate or the resulting funds. If my acts in life and the works I've made do not stand on their own, then I don't deserve one; if they do, I don't need one.
\end{enumerate}

\subsection*{Article 6: Personal Requests}\label{article-6-personal-requests}

\subsubsection*{Section 1: Notifications}\label{section-1-notifications}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Names and addresses of individuals to contact are provided in a separate signed document in the same location as this will.
\item
  Some notifications may be completed over email.
\item
  MUCK accounts are more difficult, but I have a few friends on there that deserve to know what happened, but am not in contact with elsewhere. Preferably, find a friend (Indi, Kauko, Krinn, etc) who can connect and notify those individuals and provide a link to a publicly available obituary or news article.
\end{enumerate}

\subsubsection*{Section 2: Services, Obituaries, or Articles}\label{section-2-services-obituaries-or-articles}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Please do not be shy in mentioning furry. This subculture means a hell of a lot to me, I don't want that downplayed.
\item
  Please do not be shy about poly. I love my polycule, and others besides. Reducing my relationships to the one that's legally binding would be an insult.
\end{enumerate}

\subsubsection*{Section 3: Final Notes}\label{section-3-final-notes}

\begin{itemize}
\tightlist
\item
  The Polycule as mentioned in this document is not the full thing. To other members, I apologize for not listing you; these three just have the most tangible connection to me and my goods.
\item
  Any attempt to memorialize me under my deadname will result in haunting. It won't be pleasant: I know how to be loud if need be. Don't do it.
\end{itemize}

\subsection{Signatures}

\begin{Form}
    \q{Signed}
\end{Form}

Dated this \emph{nineteenth} day of \emph{April, 2018}.

\begin{quote}
The declarer has been personally known to me and I believe her to be of sound mind. In addition, I am not the attending physician, an employee of the attending physician or health care facility in which the declarer is a patient, or any person who has a claim against any portion of the estate of the declarer upon the declarer's decease at the time of the execution of this will.
\end{quote}

\begin{Form}
    \q{Witness 1}
    \q{Witness 2}
\end{Form}

\end{document}
