\documentclass[letterpaper]{memoir}

\usepackage[top=1in, left=1in, bottom=1in, right=1in]{geometry}
\pagestyle{empty}
\renewcommand{\baselinestretch}{1.25}

\usepackage{fontspec}
\setmainfont{Gentium Book Basic}

\usepackage[usenames, dvipsnames]{color}
\definecolor{titlegreylight}{gray}{0.5}
\definecolor{titlegreydark}{gray}{0.4}

\usepackage{wrapfig}
\usepackage{xltxtra}

\begin{document}

\input{content-header}

\noindent\textit{\large Madison Scott-Clary} is an author, technical writer, and editor living in Everett, WA. She works heavily with both fiction and non-fiction in an authorial and editorial role. She strives to further her knowledge within both areas, as well as to expand into other fields both within and outside of writing and editing.

\noindent She is also a software engineer, working heavily with web development, both on the front- and back-end as well as with DevOps and cloud-based solutions. She strives to continue her growth in software, as well as to expand into other fields both within and outside of software engineering and computers. As a supporter and proponent of Free and Open-Source Software, she is committed to providing the best tools and products that she can using FOSS and under OSI-approved licenses where appropriate.


\section*{Editorial}

\input{content-editorial}

\section*{Software and technology}

\input{content-tech}

\subsection{Portfolio}

\begin{description}
  \tightlist
  \item[Writing] Madison's editorial and publishing experience is shown most clearly at Hybrid Ink, LLC. Additionally, she has published six books of her own and appeared in several others.

  \begin{itemize}
    \tightlist
    \item hybrid.ink/about
    \item makyo.ink
  \end{itemize}
  \item[Tech] As a proponent of open source software, much of Madison's code is freely available.

  \begin{itemize}
    \tightlist
    \item github.com/makyo
    \item launchpad.net/\textasciitilde{}makyo
  \end{itemize}
\end{description}

\subsection{Education}\label{education}

\begin{description}
\tightlist
\item[University] \hfill
\begin{itemize}
\tightlist
\item
Colorado State University (2004-2011) Bachelor of Music (music composition) studying music composition and computer science.
\item
Cornell College (2021-present) Master of Fine Arts (creative writing) studying fiction and creative non-fiction with an emphasis on writing education
\end{itemize}
\end{description}

Additional employment experience, publications, and volunteer projects
Madison has worked with are available on request.

\end{document}
