When I was beginning my work in software, I was added to the part of our team that helped out with interviews. A lot of technical interviews follow a similar rubric --- tell us about your past, here are some technical questions, tell us about your expectations, and ``any questions?'' --- but often, there's that one little meta question snuck in to help the team understand how the prospective employee actually \emph{works}. Here was mine:

\begin{quotation}
    \noindent You're in an airplane hangar, and before you is a mid-size plane. How do you find out how much it weighs?
\end{quotation}

The answer\footnote{We got some pretty inventive ones. My favorite was ``cut all of the plane's components in half until I can pick them up, because I know how much I can lift at once.''} we got most often --- indeed, the answer we actually wanted --- was ``I figure out what kind of plane it is and then look up the information.''

There is a wealth of information out there in the world. Wikipedia, Google, and, of course, Stack Overflow are invaluable sources for software developers. In the course of one's workday, one is presented with problems by the very definition of one's job. Often, these problems are not of the type that one can just solve off the top of one's head, despite the knowledge one has going into the task, and so the core competency I have looked for at every company I've had the privilege of working for has been not just ``how efficiently do you invert a binary tree'' but ``how well do you learn''.

Stack Overflow has quickly built itself up into a resource of incredible value, and it would be an honor to help it become the best that it can be. My project management credentials are slim, yes, but having spent so much time as an engineer, I'm well acquainted with the implementation side of the process, and hope to use that knowledge to be more effective at my position.

As I advance my career, taking a leadership role on a project I really believe in grows more and more important to me. The company provides a service I and so many others could not get by without and, whether or not I wind up at Stack Overflow, we all thank you for that.
