As an open source software developer, GitHub has come to play a very important role in my day-to-day life. It's where I turn when I need to work with my software, serve my projects, and engage with my community. I deal with GitHub or its projects (writing this from Atom!) on a daily basis.

I have been working with software development seriously for the last eighteen years --- longer if you count my mom's copy of VisualBasic 4 she let me play around with in middle school --- so the process of working with code is something that's important to me. I feel that I can bring my experience and energy to GitHub.

I have worked with the site for over six years. My background lies in web development, using Python, Groovy, Go, Javascript, CoffeeScript, and Elm. Beyond experience, I hope that I can also bring my energy and willingness to learn to the team, working to complete a project the right way, instead of just the fastest way.

As a process maven, I am experienced and adamant about CI, test coverage and reporting, and code documentation. I have also worked with technical writing, blogging, and promotional writing for software products. I have experience working in a management, mediator, and technical lead capacity, and am keenly interested in a diverse workforce, healthy work-life balance, and constructive social interactions within the workplace. As a transgender woman, I am very focused on gender representation in tech.

I look forward to hearing back from you and learning all the more about the position and life working at GitHub.
